On the performance of the MAC model

### 2018-10-30 2018_nips_vigil/introduction.tex
references mac section

To solve this type of reasoning task, many approaches have been explored although they often appear to struggle performing well on tasks with a structured and compositional nature (Garnelo et al., 2016; Lake et al., 2017). \tk{I have no idea what those papers are...}
More recent approaches adopt modular structures, resembling the trees of programming languages, that compose neural modules from a fixed predefined collection (andreas2016learning; johnson2017inferring, mascharka2018transparency). However, they rely on externally provided structured representations and functional programs, parsers or expert demonstration, and sometimes require reinforcement learning training schemes
These models’ structure is inherently rigid and the use of a range of specialized modules weaken their robustness and generalization capacities.
\tk{Compositional models are one major direction of research in VQA... but there are 3 others (including e.g. attention) that we do not mention here, thus my concern is that the above is not well balanced... I can add more when we will understand how much space is left.}

>>>>

To solve this type of reasoning task, many approaches have been explored although they often appear to struggle performing well on tasks with a structured and compositional nature \citep{hudson2018compositional}.
More recent approaches adopt modular structures, resembling the trees of programming languages, that compose neural modules from a fixed predefined collection \cite{andreas2016learning,johnson2017inferring, mascharka2018transparency}. However, they rely on externally provided structured representations and functional programs, parsers or expert demonstration, and sometimes require reinforcement learning training schemes
These models’ structure is inherently rigid and the use of a range of specialized modules weaken their robustness and generalization capacities.
\tk{Compositional models are one major direction of research in VQA... but there are 3 others (including e.g. attention) that we do not mention here, thus my concern is that the above is not well balanced... I can add more when we will understand how much space is left.}

### 2018-10-30 2018_nips_vigil/mac.tex
references mac section

By going through this recurrent process, the network performs a reasoning strategy that learns concepts and relations between them. MAC is performing state of the art accuracy on CLEVR and CLEVR Humans datasets.
In contrast to modular approaches (Andreas et al., 2016a;b; Hu et al., 2017; Johnson et al., 2017b), MAC is fully
differentiable and does not require additional supervision. It is making use of a single computational cell chained in sequence rather than a collection of custom modules deployed in a rigid tree structure.
In contrast to augmented CNN approaches (Santoro et al., 2017; Perez et al., 2017),  the MAC model provides an ability for relational reasoning with better generalization capacity, higher
computational efficiency and enhanced transparency.

>>>>

By going through this recurrent process, the network performs a reasoning strategy that learns concepts and relations between them. MAC is performing state of the art accuracy on CLEVR and CLEVR Humans datasets.
In contrast to modular approaches \cite{andreas2016learning,hu2017learning,johnson2017inferring}, MAC is fully
differentiable and does not require additional supervision. It is making use of a single computational cell chained in sequence rather than a collection of custom modules deployed in a rigid tree structure.
In contrast to augmented CNN approaches, the MAC model provides an ability for relational reasoning with better generalization capacity, higher
computational efficiency and enhanced transparency \cite{hudson2018compositional}.
